Appendix

### 2021-05-04 paper/preprint/paper_revised_submission_april2021_apa.Rmd
minor intro edits
reworking sections to accomodate new bb analyses

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
                      include:
                        after_body: appendix.tex
---

@@

```{r}
## Read in data 
load(here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
```

```{r}
# load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021.RData')) # gold sample detections
load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations

load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_all_detections.RData'))

@@

## Dataset
The dataset is described in detail in @SAYcam; we summarize these details here. Children wore Veho Muvi miniature cameras mounted on a custom camping headlamp harness ("headcams") at least twice weekly, for approximately one hour per recording session. One weekly session was on the same day each week at a roughly constant time of day, while the other(s) were chosen arbitrarily at the participating family’s discretion. At the time of the recording, all three children were in single-child households.  Videos captured by the headcam were 640x480 pixels, and a fisheye lens was attached to the camera to increase the field of view to approximately 109 degrees horizontal x 70 degrees vertical. Videos ^[All videos are available at https://nyu.databrary.org/volume/564 ] with technical errors or that were not taken from the egocentric perspective were excluded from the dataset.  We analyze `r num_videos` videos, with a total duration of `r round(num_hours,2)` hours (>50 million frames).

@@

## Detection Validation

```{r}
# Function to evaluate detectors
evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

@@

 ## output prfs
 face_performance = return_prf_short(gold_sample$face_eval_ketan)
 hand_performance = return_prf_short(gold_sample$hand_eval_ketan)

```{r}
## for high confidence detections
gold_sample_hc <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op_hc) %>% # HIGH CONF DF
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))

face_performance_hc = return_prf_short(gold_sample_hc$face_eval_ketan)
hand_performance_hc = return_prf_short(gold_sample_hc$hand_eval_ketan)
```

@@

To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A); XX frames with allocentric videos were excluded, as were these videos from the rest of analyses. Frames were jointly annotated for the presence of faces and hands by one author. A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated 3150 frames; agreement with the primary coder was >95%.

@@

To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (the harmonic mean of precision and recall).  In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`. For hands, the F-score was `r round(hand_performance[3],2)`, with a precision of `r round(hand_performance[1],2)` and recall of `r round(hand_performance[2],2)`. While face and hand detections showed moderately good precision, face detections were overall slightly more accurate than hand detections.  In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset. 
We also evaluated OpenPose's performance while restricting detections to high-confidence detections (>.5 confidence, default threshold for visualization). For faces, we found that the F-score was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`. For hands, the F-score for high confidence detections `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`. Thus, as in prior work [@long2020automated], while precision was much highe for both faces and hands, the lower recall for high-confidence detection indicates that these lower-confidence detections still index the presence of social information in the infant view.

@@

```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_faces_with_hands = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_hands_with_faces = sum(faces_and_hands, na.rm=TRUE)/num_hands 
            )

@@

We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands that were in view for each child.^[All analyses and preprocessed data files for this paper are available at https://tinyurl.com/detecting-social-info] Data from videos were binned according to the age of the child (in weeks). First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:FacesAndHands}); in contrast, we did not observe an increase in the proportion of hands in view, but rather a slight decrease. These effects were quantified with two separate linear mixed-models (see Tables 1 & 2).^[Face/hand detections were binned across each week of filming. Participant's age was converted into months and centered for these analyses. Random slopes for the effect of age by child led to a singular fit and were removed from both analyses; see full model specification in accompanying codebase.]

However, the most striking result from these analyses is a much overall greater proportion of hands in view than have previously been reported [@Fausey2016]. We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Appendix Figure \ref{fig:goldSetSanity}) or OpenPose annotations on the entire dataset (see solid lines in Figure \ref{fig:FacesAndHands}). This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may be an underestimate of the proportion of hands in view. Nonetheless, one reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees. This larger FOV may have allowed the SAYCam cameras to capture not only the presence of a social partner’s hands interacting with objects or gestures, but also the children’s own hands, leading to more frequent hand detections.

As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center)/sum(all_vid_data$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center)/sum(all_vid_data$num_frames),3)*100`%. This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view. Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:FacesAndHands}).

In a second set of analysis, we explored finer-grained changes in the ways in which infants’ experienced this social information across development, capitalizing on the fact that OpenPose provides not only face and hand detections but also positional keypoints. In particular, we explored this dataset with the idea that younger children may tend to see larger, complete faces towards the center of their visual field—that is, that have both eyes, nose, and a mouth in view—while older children may experience more incomplete views of faces.

First, we explored the proportion of faces that were detected that tended to be “complete” faces—that is, faces where the eyes, mouth, and nose were all detected by OpenPose. Figure \ref{eye_distance} shows that roughly half of the faces detected by OpenPose were full-view faces, suggesting that infants’ are often seeing partial views of their caregiver’s faces. More generally, we found that the proportion of full faces in view roughly followed the proportion of faces in view, again converging with the findings of Fausey et al., 2016 showing a decrease in the proportion of faces in the infant view across early development.

```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of face, hand, 'full' face (i.e. nose, mouth, and nose visilbe), and joint face/hand detections as a function of age for each child in the dataset. Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range. }
ggplot(face_hand_detailed_plot, 
       aes(x=age_day_bin, y=prop, 
           col=region)) +
  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(.~child_name) + 
  theme_few(base_size=12) +
  scale_color_manual(values = c( "#2048d6","#d62020","#751098","#142c83"), name = "") +
  scale_size_continuous(name = "") +
  guides(size = FALSE) +
  theme(legend.text=element_text(size=8)) +
  theme(legend.position="bottom") 
```

```{r}
# eye distance... ugh
eye_dist <- all_vid_data %>%
  group_by(child_id, age_day_bin) %>%
  summarize(eye_distance = mean(avg_eye_distance, na.rm=TRUE), num_frames_total = sum(num_frames)) %>%
  filter(num_frames>2000)
```

```{r avgEyeDistance, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Average distance between eyes in faces detected as a function of age for each child in the dataset (each color = different child). Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range. }
ggplot(eye_dist, 
       aes(x=age_day_bin, y=eye_distance, 
           col=child_id)) +
  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
  geom_smooth(method='lm', aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Average distance between eyes') + 
  xlab('Age (Months)') +
  theme_few(base_size=12) +
  scale_color_brewer(palette="Dark2") +
  guides(size = FALSE) +
  theme(legend.text=element_text(size=12)) +
  theme(legend.position="none", aspect.ratio=.75) 
```

```{r}
# eye distance... ugh
face_hand_contingency <- face_hand_by_age %>%
  pivot_longer(c(prop_faces_with_hands, prop_hands_with_faces), values_to="prop", names_to = "region") %>%
  mutate(region = case_when(
    region == "prop_faces_with_hands" ~ "Proportion hands (given face detection)",
    region == "prop_hands_with_faces" ~ "Proportion faces (given hand detection)"))
```

```{r faceHandContingency, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=5, fig.height=3, fig.cap = "Face hand contingnecy }
ggplot(face_hand_contingency, 
       aes(x=age_day_bin, y=prop, 
           col=child_id)) +
  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
  geom_smooth(method='lm', aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Average distance between eyes') + 
  xlab('Age (Months)') +
  theme_few(base_size=12) +
  facet_grid(~region) +
  scale_color_brewer(palette="Dark2") +
  guides(size = FALSE) +
  theme(legend.text=element_text(size=12)) +
  theme(legend.position="none", aspect.ratio=.75) 
```

In addition, we found faces tended to be farther away from children across age (restricting our analysis to faces where both eyes were detected). Figure X shows the average interpupillary distance on faces as a function of each child’s age at the time of recording, showing a trend from larger, closer faces (with a larger interpupillary distance) to smaller faces that were farther away (with a smaller interpupillary distance). We saw relatively similar trends across all three children in the dataset, and a linear mixed-effect model confirmed a main effect of age (STATS; see repository for full model specification). However, when we examined the size of all faces and hands in the infant view, we found consistency across development (see Appendix, Figure X): while faces (and full body poses) were of course bigger than hands on average, these properties were relatively stable across development and children (see Appendix, Figure X).

Next, we explored where in the visual field children tended to see faces and hands, suspecting, perhaps, that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank, 2012.  As expected, faces tended to appear in the upper visual field vs. hands, which tended to be more centrally located. Figure XX shows the average position of faces and hands in the visual field; each dot represents the average position from one video within a given age range. However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ -- and likely adults’ -- visual environment from 6 months of age.

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept)  9.845e-02  1.049e-02  1.956e+00   9.386  0.01198 * 
Age   -1.418e-03  4.503e-04  4.310e+02  -3.150  0.00175 **
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of faces seen by infants in the center FOV.} 
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept)  1.612e-01  8.930e-03  1.881e+00   18.05   0.0040 **
Age   -9.987e-04  5.945e-04  4.287e+02   -1.68   0.0937 
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of hands seen by infants in the center FOV.} 
\end{table}

## Access to social information in different locations
```{r}
load(here::here('data/data_preprint/saycam_metadata.RData')) # meta

@@

```{r DetByLocation, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands by location in which egocentric videos were filmed; each panel represents data from an individual child (location annotations were not yet available for Y). Each dot represents data from a week in which videos were filmed and are scaled by the number of frames."}

@@

How does variability across different contexts influence the social information in the infant view? Intuitively, some activities in different contexts may be characterized by a much higher proportion of faces (e.g., diaper changes in bedrooms) than others (e.g., playtime in the living room). We thus next examined variation in presence of hands and faces across different locations. Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location they were filmed in. Of these, `r videos_included` videos were filmed in single location, representing 17 percent of the dataset and over 5 million frames. Activities varied somewhat predictably by these contexts: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room. Overall, we found that the proportion of faces vs. hands varied across filming locations, and, to some extent, across children; separate chi-squared tests for each child and detection type revealed significant variability in detections by location in each case ^[all *p*<.001, see accompanying codebase]. For example, while both A and S saw a relatively similar proportion of faces vs. hands in the bedroom, they saw quite different amounts of faces vs. hands in kitchens (see Figure \ref{fig:DetByLocation}).

# General Discussion
Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the proportion of hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age. This analysis has yielded a better understanding of infants' evolving access to social information. We found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016]. This finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018].

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

```{r}
# Read in data 
## Face/hand detections by video
load(here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
```

```{r}
# load bounding box summaries by video
load(file=here::here('data/preprocessed_data_2021/bounding_box_summaries_all.RData'))
```

```{r}
# gold sample annotatios and detedctinos for these specific frames
load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_all_detections.RData'))

@@

## Dataset
The dataset is described in detail in @SAYcam; we summarize these details here. Children wore Veho Muvi miniature cameras mounted on a custom camping headlamp harness ("headcams") at least twice weekly, for approximately one hour per recording session. One weekly session was on the same day each week at a roughly constant time of day, while the other(s) were chosen arbitrarily at the participating family’s discretion. At the time of the recording, all three children were in single-child households.  Videos captured by the headcam were 640x480 pixels, and a fisheye lens was attached to the camera to increase the field of view to approximately 109 degrees horizontal x 70 degrees vertical. Videos ^[All videos are available at https://nyu.databrary.org/volume/564 ] with technical errors or that were not taken from the egocentric perspective were excluded from the dataset.  We analyze `r num_videos` videos, with a total duration of `r round(num_hours,2)` hours (>40 million frames).

@@

## Detection Validation
```{r}
# Function to evaluate detectors
evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

@@

 ## output prfs
 face_performance = return_prf_short(gold_sample$face_eval_ketan)
 hand_performance = return_prf_short(gold_sample$hand_eval_ketan)
```

```{r eval=FALSE,include=FALSE}
## for high confidence detections
# gold_sample_hc <- gold_sample %>%
#   select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
#   mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
#   right_join(all_gold_sample_frames_op_hc) %>% # HIGH CONF DF
#   mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))
# 
#  
# face_performance_hc = return_prf_short(gold_sample_hc$face_eval_ketan)
# hand_performance_hc = return_prf_short(gold_sample_hc$hand_eval_ketan)
```

@@

To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A); `r  24000-length(gold_sample$face_openpose)` frames with allocentric videos were excluded, as were these videos from the rest of analyses. Frames were jointly annotated for the presence of faces and hands by one author. A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated 3150 frames; agreement with the primary coder was >95%.

@@

To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (the harmonic mean of precision and recall).  In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`. For hands, the F-score was `r round(hand_performance[3],2)`, with a precision of `r round(hand_performance[1],2)` and recall of `r round(hand_performance[2],2)`. While face and hand detections showed moderately good precision, face detections were overall slightly more accurate than hand detections.  In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.

@@

```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_joint_given_faces = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_joint_given_hands = sum(faces_and_hands, na.rm=TRUE)/num_hands,
            prop_joint_given_faces_center = sum(face_and_hands_center, na.rm=TRUE)/num_faces_center, 
            prop_joint_given_hands_center = sum(face_and_hands_center, na.rm=TRUE)/num_hands_center)

@@

We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands detected for each child.^[All analyses and preprocessed data files for this paper are available at https://tinyurl.com/detecting-social-info] Data from videos were binned according to the age of the child (in weeks). First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:FacesAndHands}), in keeping with prior findings [@Fausey2016]; in contrast, we did not observe an increase in the proportion of hands in view. These effects were quantified with two separate linear mixed-models (see Tables 1 & 2).^[Face/hand detections were binned across each week of filming. Participant's age was converted into months and centered for these analyses. Random slopes for the effect of age by child led to a singular fit and were removed from both analyses; see full model specification in accompanying codebase.]

However, the most striking result from these analyses is a much overall greater proportion of hands in view than have previously been reported [@Fausey2016]. We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Appendix Figure \ref{fig:goldSetSanity}) or OpenPose annotations on the entire dataset (see solid lines in Figure \ref{fig:FacesAndHands}). This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may be an underestimate of the proportion of hands in view. In fact, analysis the human annotations underscores revealed a much higher proportion of hands relative to faces than the automated annotations.

One reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees. This larger FOV may have allowed the SAYCam cameras to capture not only the presence of a social partner’s hands interacting with objects or gestures, but also the children’s own hands, leading to more frequent hand detections.

As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%. This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view. Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:FacesAndHands}). We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure\ref{fig:goldSetSanity}).

Finally, we analyzed how these two sources of social information co-occurred, finding  that faces/hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}). To do so, we  calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range. We found that all three infants than were more likely see hands independently -- without the presence of a face -- that they were likely to see faces independently. That is, generally speaking when a face was present, a hand also tended to be present.

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 0.098 & 0.010 & 1.956 & 9.386 & 0.012 \\ 
  age\_scale & -0.001 & 0.000 & 430.976 & -3.150 & 0.002 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of faces seen by infants in the center FOV.} 
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 0.161 & 0.009 & 1.881 & 18.046 & 0.004 \\ 
  age\_scale & -0.001 & 0.001 & 428.651 & -1.680 & 0.094 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of hands seen by infants n the center FOV.} 
\end{table}

```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of face, hand, 'full' face (i.e. nose, mouth, and nose visilbe), and joint face/hand detections as a function of age for each child in the dataset. Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range." }
ggplot(face_hand_detailed_plot, 
       aes(x=age_day_bin, y=prop, 
           col=region)) +
  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(.~child_name) + 
  theme_few(base_size=12) +
  scale_color_manual(values = c( "#2048d6","#d62020","#751098","#142c83"), name = "") +
  scale_size_continuous(name = "") +
  guides(size = FALSE) +
  theme(legend.text=element_text(size=8)) +
  theme(legend.position="bottom") 
```

```{r}
face_hand_contingency <- face_hand_by_age %>%
  pivot_longer(c(prop_joint_given_hands, prop_joint_given_faces), values_to="prop", names_to = "region") %>%
  mutate(region = case_when(
    region == "prop_joint_given_faces" ~ "Prop. hands (given face det)",
    region == "prop_joint_given_hands" ~ "Prop. faces (given hand det)"))

    # region == "prop_joint_given_faces_center" ~ "Prop. center hands (given center face det)",
    # region == "prop_joint_given_hands_center" ~ "Prop. center faces (given center hand det)"))
```

```{r faceHandContingency, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of joint face/hands detection within frames where frames/ were detected." }
face_hand_contingency_plot <- ggplot(face_hand_contingency, 
       aes(x=age_day_bin, y=prop, 
           col=child_id)) +
  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Proportion joint hand/face detection') + 
  xlab('Age (Months)') +
  theme_few(base_size=12) +
  facet_grid(~region) +
  # scale_color_manual(values = c( "#DAA0EE","#710D93"), name="") +
  scale_color_brewer(palette="Dark2") +
  guides(size = FALSE) +
  theme(legend.text=element_text(size=12)) 
```

## Variability in social information across learning contexts 
```{r}
load(here::here('data/data_preprint/saycam_metadata.RData')) # meta

@@

```{r DetByLocation, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=5, fig.cap = "Proportion of faces and hands by location in which egocentric videos were filmed; each panel represents data from an individual child (location annotations were not yet available for Y). Each dot represents data from a week in which videos were filmed and are scaled by the number of frames."}

@@

How does variability across different learning contexts influence the social information in the infant view? Intuitively, some activities in different contexts may be characterized by a much higher proportion of faces (e.g., diaper changes in bedrooms) than others (e.g., playtime in the living room). We thus next examined variation in presence of hands and faces across different locations. Of the `r num_videos` videos, `r num_videos_annotated` were annotated [@SAYcam] for the location they were filmed in. Of these, `r videos_included` videos were filmed in single location, representing 17 percent of the dataset and over 5 million frames. Activities varied somewhat predictably by these contexts: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room. Overall, we found that the proportion of faces vs. hands varied across filming locations, and, to some extent, across children; separate chi-squared tests for each child and detection type revealed significant variability in detections by location in each case ^[all *p*<.001, see accompanying codebase]. For example, while both A and S saw a relatively similar proportion of faces vs. hands in the bedroom, they saw quite different amounts of faces vs. hands in kitchens (see Figure \ref{fig:DetByLocation}).

## Fine-grained changes in the social information in view
```{r}
## construct age bins for plotting
bin_size=7
min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
max_age = max(all_vid_bbs$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

all_vid_bbs <- all_vid_bbs %>%
  mutate(age_months = age_days/30.4) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))  %>%
 mutate(avg_center_y = avg_top + avg_height/2, avg_center_x = avg_left + avg_width/2) %>%
  filter(!avg_area==0) # a very few bounding boxes with zero areas (all keypoints on one plane as faces
```

```{r}
# Changes in full vs. all faces? --- not significant, inconsistent results across kids
# diff_full_vs_all <- face_hand_by_age %>%
#   mutate(diff = prop_faces - prop_full_faces)
#
# ggplot(diff_full_vs_all, aes(x=age_day_bin, y=diff, color=child_id, size=num_frames_total)) +
#   geom_point(alpha=.2) +
#   geom_smooth(method='lm')
#
# summary(lmer(data=diff_full_vs_all, diff ~ scale(age_day_bin) + scale(num_frames_total) + (1|child_id)))
```

```{r}
# for plotting average area / age for each type 
avg_area_by_age <- all_vid_bbs %>%
  group_by(age_day_bin, child_id, label) %>%
  summarize(avg_area = mean(avg_area), num_detect = sum(num_detect)) %>%
  mutate(label = factor(label, levels = c('pose','face','hand'), labels = c('Full body pose','Faces','Hands'))) %>%
  mutate(child_id = as.factor(child_id))
```

```{r avgSizes, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Average size of poses, faces, and hands detected in the dataset  between eyes in faces detected as a function of age for each child in the dataset (each color = different child). Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range."}

ggplot(avg_area_by_age, aes(x=age_day_bin, y=log(avg_area), col=child_id, size=num_detect)) +
  geom_point(alpha=.1) +
  facet_grid(~label) +
  geom_smooth(method='lm') + 
  ylab('Log (average area)') +
  xlab('Age in days') +
  scale_color_brewer(palette="Dark2", name = "Child") +
  guides(size = FALSE)
```

```{r}
# eye distance dataframe
eye_dist <- all_vid_data %>%
  group_by(child_id, age_day_bin) %>%
  summarize(eye_distance = mean(avg_eye_distance, na.rm=TRUE), num_faces = sum(num_faces)) %>%
  filter(num_faces>2000) %>%
  mutate(variable = 'Eye distance')
```

```{r}
eye_dist_plot <- ggplot(eye_dist, 
       aes(x=age_day_bin, y=eye_distance, 
           col=child_id)) +
  geom_point(alpha=.15, aes(size=num_faces), show.legend= FALSE) +
  geom_smooth(method='lm', aes(weight = num_faces), show.legend = TRUE) + 
  ylab('Avg. distance between eyes') + 
  xlab('Age (in months)') +
  theme_few(base_size=12) +
  facet_grid(~variable) +
  scale_color_brewer(palette="Dark2", name='Child') +
  guides(size = FALSE) +
  ggtitle('A.') +
  theme(legend.text=element_text(size=12))  +
  theme(legend.position="none")
```

```{r} 
CV_faces <- all_vid_bbs %>%
  filter(label=='face') %>%
  group_by(age_day_bin,child_id) %>%
  summarize(cv_x_pos = sd(avg_center_x)/mean(avg_center_x)*100, cv_y_pos = sd(avg_center_y)/mean(avg_center_y)*100, num_detect = sum(num_detect), avg_size = mean(avg_area), num_vids = n(), avg_x_pos = mean(avg_center_x), avg_y_pos = mean(avg_center_y)) %>%
  pivot_longer(cols = c(cv_y_pos, cv_x_pos), values_to = "CV", names_to = "position") %>%
  mutate(position = factor(position, levels = c("cv_x_pos","cv_y_pos"), labels = c("Face X Position", "Face Y Position")))

```{r}
CV_faces_plot <- ggplot(CV_faces, aes(x=age_day_bin, y = CV, size=num_detect, color=child_id)) +
  geom_point(alpha=.15) + 
  facet_wrap(~position)  +
  geom_smooth(method='lm') +
  ggtitle('B.') +
  scale_color_brewer(palette='Dark2', name='Child') + 
  ylab('Coefficient of variation') +
  xlab('Age (in months)') +
  guides(size = FALSE) 
```
